Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-16 paper.qmd
Removed prediction codes

# df_bin_centroids_two_curvy <- df_bin_centroids_two_curvy |>
#   dplyr::filter(std_counts > 0)

@@

proj_obj1 <- quollr::get_projection(projection = model_prj1, 
               proj_scale = 1, 
               highd_data = scaled_two_curvy_data, 
               model_highd = scaled_two_curvy_data_model, 
               trimesh_data = tr_from_to_df_two_curvy, 
               axis_param = list(limits = 0.5, 
                                 axis_scaled = 2,
                                 axis_pos_x = -0.5, 
                                 axis_pos_y = -0.5, 
                                 threshold = 0.03))

@@

```{r}
#| label: fig-two-curvy-true-proj
#| fig-cap: "Two \\gD{} projections from \\fD{}, for the two nonlinear clusters data (blue points) and true model (black lines) are shown. The top cluster in (a) shows uniformly distributed data along a C-shape, while in the bottom cluster, the data is more concentrated in one corner of the curvy shape. Video of the langevitour animations are available at <>." 
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5
#| eval: false

two_curvy_proj_true + two_curvy_proj_true2 +
  plot_layout(ncol = 2)
```

@@

<!--prediction for true-model of two-curvy clust-->
```{r}
#| label: model-prediction-umap-original

predict_tsne_two_curvy <- read_rds(file = "data/two_non_linear_diff_shaped_close_clusters/two_non_linear_diff_shaped_close_clusters_umap_predict_true.rds")

predict_two_curvy_obj <- gen_scaled_data(
    nldr_data = predict_tsne_two_curvy)

predict_tsne_two_curvy_scaled <- predict_two_curvy_obj$scaled_nldr

plot_predict_umap_fun_two_curvy <- ggplot(
  data = predict_tsne_two_curvy_scaled, 
  aes(x = UMAP1, 
      y = UMAP2)) +
  geom_point(alpha = 0.5) +
  interior_annotation("b", c(0.08, 0.93), cex = 1.5)
```

```{r}
#| label: model-prediction-points-line
#| eval: false

predict_tsne_two_curvy_scaled <- predict_tsne_two_curvy_scaled |>
  mutate(ID = row_number()) |>
  mutate(type = "predict_from_umap")

jittered_points_df <- jittered_points_df |>
  mutate(type = "predict_from_model")

predict_point_df <- bind_rows(
  predict_tsne_two_curvy_scaled,
  jittered_points_df
)

plot_predict_umap_connect_two_curvy <- ggplot(
  data = predict_point_df, 
  aes(x = UMAP1, 
      y = UMAP2, 
      group = ID)) +
  geom_point(alpha = 0.5) +
  geom_line(alpha = 0.3) +
  interior_annotation("d", c(0.08, 0.93), cex = 1.5)
```

```{r}
#| echo: false
#| label: fig-predict-two-curvy
#| fig-pos: H
#| fig-width: 10
#| fig-height: 10
#| out-width: 80%
#| fig-cap: "Comparison of prediction generated using the exiting `umap` R package's prediction method and our method: (a) A view of the true model in projection from $7\\text{-}D$, (b) predicted data from the `umap` prediction method, and (c) predicted data from our method."
#| eval: false

proj_plot_two_curvy_true + plot_predict_umap_fun_two_curvy +plot_predict_tsne_two_curvy +
  plot_layout(ncol = 3)
```

>>>>

@@

proj_obj1 <- get_projection(projection = model_prj1, 
               proj_scale = 1, 
               highd_data = scaled_two_curvy_data, 
               model_highd = scaled_two_curvy_data_model, 
               trimesh_data = tr_from_to_df_two_curvy, 
               axis_param = list(limits = 0.5, 
                                 axis_scaled = 2,
                                 axis_pos_x = -0.5, 
                                 axis_pos_y = -0.5, 
                                 threshold = 0.03))

@@

@@
